Figures to insert in text

### 2018-04-15 Chapters/Chapter02.tex
Bongard problem citations

@@

\section{Deep learning, multiple SDMs, and the incredible animal behavior of Dr. Linhares}

@@

    Those deep neural networks... alphaGo... alphazero... very impressive, and to me very right and proper in a sense and also very wrong and misguided in another. I have not seriously studied the topic. Eric Nichols explained it to me in a napkin, and I watched some youtube videos and browsed the books. So what follows, like all great science, is completely based on gossip, hearsay, prejudice and anecdote.  Or at least that's how I believe all great \emph{hunches} over what is promising and what is a dead-end come from; that aesthetic sense that forms over time and seems to guide us towards what feels beautiful and correct and away from what seems foolish and wasteful...

@@

    But it feels like a mistake to say that that is thinking.  It's not.  It is to me a great model of someone getting so attuned into an area that they are able to simply flow through tasks; in the positive psychology sense of the word flow.  It's very powerful and very intelligent:  but it is a form of intelligence without thinking.  Intelligence that can't make leaps from one arena to another; Intelligence that can't work on Bongard problems.  So what I would fear as a dead-end in research would be to have decades of massive, massive number-crunching and machine learning of this type... in disregard to big questions such as the interaction of short-term memory with SDM and, again, tasks like Bongard problems (Figures \ref{fig:bongard-problems-71, fig:bongard-problems-71, fig:bongard-problems-71}).

@@

    Hofstadter has nailed the interactions and the content... analogies, fluid concepts, things seen through a different perspective, variations on a theme, etc.  Kanerva has nailed system 1, long-term-memory, and its  theoretical neuroscience; micro neuro-firings bringing a memory back to life.  Attaching something as beautiful as SDM to, say, some hyper-efficient alpha-beta pruning algorithm is nothing short of heresy against all the gods of science and must be punished with death without mercy. Seems like the most reasonable path going forward...

>>>>

highway hypnosis; absentminded driving; Going on Autopilot; PNAS study

@@

\section{Deep learning, multiple SDMs --- and the incredible animal behavior of Dr. Linhares}

@@

    Those deep neural networks... alphaGo... alphazero... very impressive, and to me very right and proper in a sense and also very wrong and misguided in another. I have not seriously studied the topic. Eric Nichols explained it to me in a napkin, and I watched some youtube videos and browsed the books. So what follows, like all great science, is completely based on gossip and hearsay, prejudice and anecdote.  Or at least that's how I believe all great \emph{hunches} over what is promising and what is a dead-end come from; that aesthetic sense that forms over time and seems to guide us towards what feels beautiful and correct and away from what seems foolish and wasteful...

@@

    But it feels like a mistake to say that that is thinking.  It's not.  It is to me a great model of someone getting so attuned into an area that they are able to simply flow through tasks; in the positive psychology sense of the word flow.  It's very powerful and very intelligent:  but it is a form of intelligence without thinking.  Intelligence that can't make leaps from one arena to another; Intelligence that can't work on Bongard problems.  So what I would fear as a dead-end in research would be to have decades of massive, massive number-crunching and machine learning of this type... in disregard to big questions such as the interaction of short-term memory with SDM and, again, tasks like Bongard problems (Figures \ref{fig:bongard-problems-71, fig:bongard-problems-74, fig:bongard-problems-77}; see \citet{bongard_recognition_1968, douglas1980godel, Linhares2000, foundalis_phaeaco:_2006, lupyan_difficulties_2013}).

@@

    Hofstadter has nailed the interactions and the content... analogies, fluid concepts, things seen through a different perspective, variations on a theme, etc.  Kanerva has nailed system 1, long-term-memory, and its  theoretical neuroscience; micro neuro-firings bringing a memory back to life.  Attaching something as beautiful as SDM to, say, some hyper-efficient centralized alpha-beta pruning algorithm is nothing short of heresy against all the gods of science for which the villain must be put to death without mercy. Seems like the only reasonable path going forward...

### 2018-04-15 Chapters/sdm-autocorrelation.tex
Bongard problem citations

This is an important observation. A hard location is activated because it shares many dimensions with the items read from or written onto it. Imagine the `counter's eye view':  each individual counter `likes' to write on its own corresponding bit-address value more than it likes the opposite; as each hard-location has a say in its own area --- and nowhere else.

>>>>

This is an important observation. A hard location is activated because it shares many dimensions with the items read from or written onto it. Imagine the `counter's eye view':  each individual counter `likes'\footnote{If I were a cell I would try to avoid the neighborhood of a neuron. Neurons have serious authoritarian tendencies, violently bossing innocent cells around --- sometimes through electric shocks.} to write on its own corresponding bit-address value more than it likes the opposite; as each hard-location has a say in its own area --- and nowhere else.
